### 2025-04-16 multiple-regression.qmd
20250416 - absolute value of direct and indirect effects

We can calculate this by substituting in the regression coefficients and predictor values:

Here is the computation:

@@

  # total effect (c)
  total := direct + indirect
'
```

@@

  # total effect (c)
  total := direct + indirectTotal
'
```

>>>>

We can calculate this by substituting in the regression coefficients and predictor values.
Here is the computation:

@@

  # total effect (c)
  total := abs(direct) + abs(indirect)
'
```

@@

  # total effect (c)
  total := abs(direct) + abs(indirectTotal)
'
```
